Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex

\begin{figure*}[bth]
		\centering
		\includegraphics[width=1\linewidth]{figures/asm_cmp.pdf}
		\caption{GCC and LLVM: different optimizations on the comparison loop}
		\label{fig:Asm}
\end{figure*}

@@

\vspace{10cm} %Adapt to make vfill work

@@

Source code of the smart syntax method, which is used to generate the C code for the plugin but also as Smalltalk fall-back code.

>>>>

\begin{figure*}[bth]
		\centering
		\includegraphics[width=1\linewidth]{figures/asm_cmp.pdf}
		\caption{GCC and LLVM: different optimizations on the comparison loop \cba{on peut enlever les adresses je pense ca sert a rien en vrai et comme ca les fonts pourront etre plus grosses}}
		\label{fig:Asm}
\end{figure*}

@@

%\vspace{10cm} %Adapt to make vfill work

@@
